MS Prelim Data K23

### 2024-07-11 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
making more grouping variables
Really trying to figure out how best to carve the EMR anxiety space

@@

@@

@@

@@

@@

@@

@@

>>>>

dep_and_anxiety_net_overlap_names_no_CC <- dep_and_anxiety_net_overlap_names[dep_and_anxiety_net_overlap_names != "CC"]
dep_and_anxiety_net_overlap_net_volume_no_CC <- sum(dep_net_overlap_from_bp_paper$num_voxels_total[dep_net_overlap_from_bp_paper$fascicle %in% dep_and_anxiety_net_overlap_names_no_CC]) #vol = 95659

@@

dep_and_anxiety_net_overlap_names_w_suff_no_CC <- dep_and_anxiety_net_overlap_names_no_CC %>% gsub(pattern = "(.*)", replacement = "\\1_vol", perl=TRUE) #take fascicles not in

@@

  ##sum of total volume lost in areas of overlap between depression + anxiety network and proportion of volume lost in network (volume lost/network volume size), no CC
  mutate(sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = 
           rowSums(across(all_of(dep_and_anxiety_net_overlap_names_w_suff_no_CC)))) %>%
  mutate(proportion_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC = sum_fascicle_vol_lost_indep_and_anxiety_net_overlap_no_CC/dep_and_anxiety_net_overlap_net_volume_no_CC) %>%

@@

### BEST SPLIT IS STRATIFYING ON ANXIETY MEDS!!!! Better than on variable that includes anxietyGroupVar(meds + anxiety diagnoses), or anxiety diagnosis alone
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietyGroupVar != 0,])
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])

@@

#Has.Anxietydx.Or.Antianxietymed
#on benzos: 0.4022933; off benzos:0.372135
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="On.Benzos"])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Has.Anxietydx.Or.Antianxietymed=="Off.Benzos"])

@@

#Anxiety network interactions and uncinate alone
```{r anxiety_net_intx}

make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$Has.Anxietydx.AND.AntianxietymedGroupVar != 0,])

#clean up data frame
cleaned_df <- df_demo_and_fascicles %>%
  filter(Has.Anxietydx.AND.AntianxietymedGroupVar != 0) %>% #lose 93, n now 719
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(Has.Anxietydx.AND.AntianxietymedGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  mutate(mean_uncinate_injury = (UF_L_prop + UF_R_prop)/2) %>%
  mutate(mean_uncinate_and_fornix_injury = (UF_L_prop + UF_R_prop + F_R_prop + F_L_prop)/2) %>%
  ungroup()

df_empi_dx_network_proportions <- cleaned_df %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#histos
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], main = "Anxiety Network Injury", xlab = "Proportion Affected")
hist(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], main = "Nonanxiety Network Injury", xlab = "Proportion Affected")
hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS+Anxiety"], main = "Uncinate Injury in Anxious Patients", xlab = "Proportion Affected")
hist(cleaned_df$mean_uncinate_injury[cleaned_df$Diagnosis == "MS-Anxiety"], main = "Uncinate Injury in Healthyish Patients", xlab = "Proportion Affected")

#t test, 
within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
within_vs_outside_anxiety_net_t

#diagnosis: 
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#t test uncinate alone
mean_uncinate_by_dx_t <- t.test(cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$mean_uncinate_injury[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
mean_uncinate_by_dx_t

#diagnosisxmean_uncinate: 
diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_injury ~ Diagnosis, data = cleaned_df)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#diagnosisxmean_uncinate+fornix: 
diagnosis_by_network_interaction_lmer <- lm(mean_uncinate_and_fornix_injury ~ Diagnosis, data = cleaned_df)
summary(diagnosis_by_network_interaction_lmer)
confint(diagnosis_by_network_interaction_lmer)

#### if I decide later I want to look at L and right uncinate alone

#t test uncinate alone, Left,
l_uncinate_by_dx_t <- t.test(cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_L_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
l_uncinate_by_dx_t

#t test uncinate alone, right, remember everybody is double counted!!!! so this needs to be fixed.
r_uncinate_by_dx_t <- t.test(cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], cleaned_df$UF_R_prop[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)
r_uncinate_by_dx_t

## Anxiety burden severity T test ranking

I am wondering here if, as my brain wants to think, that things in the chart reflect severity of anxiety. For example, I'd expect people with dep and anxiety comorbidity and on meds would be the sickest, followed by anxiety + on meds, then on meds, then anxiety dx, then healthyish. I am going to do a t-test comparing proportion of disease over whole brain, over anxiety net, and over uncinate in each of those groups as compared to the healthy group, and rank the T to see if that pattern bears out. And if it does, do some sort of regression.
```{r anxiety_burden_severity_ranking }
#variables_to_evaluate <- c("Has.Anxietydx.AND.AntianxietymedGroupVar")
df_disease_burden_unc_and_anx_net <- df_demo_and_fascicles %>%
  filter(oAnxiety.And.Dep.And.AnxietyMedsGroupVar != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex)

tibble_n <- df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>% 
  summarise(n())

tibble_overall_disease <- 
  df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(mean_size = mean(proportion_volume_lost_per_total_network_size_sum))

tibble_overall_summaries <- 
  df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- 
  df_disease_burden_unc_and_anx_net %>% 
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- 
  df_disease_burden_unc_and_anx_net %>% 
  filter(osex == "Female") %>%
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- 
  df_disease_burden_unc_and_anx_net %>% 
  filter(osex == "Male") %>%
  group_by(oAnxiety.And.Dep.And.AnxietyMedsGroupVar) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males

  ### analyses

###Collapse anxiety dx and antianxiety meds with those plus depression
```{r group_anxietydx_meds_and_dep_comorbidity}

#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression

df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
  dplyr::select(proportion_volume_lost_per_total_network_size_sum, proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75, UF_L_prop, UF_R_prop, oAnxietydx.Meds.Inc.Dep.Collapsed, osex)

 tibble_overall_summaries <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
tibble_overall_summaries

tibble_overall_summaries_by_sex <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed, osex) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_by_sex

  tibble_overall_summaries_females <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Female") %>%
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_females

    tibble_overall_summaries_males <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  filter(osex == "Male") %>%
  group_by(oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  summarize(n(),
            mean_disease_burden = mean(proportion_volume_lost_per_total_network_size_sum),
            mean_disease_burden_anxiety_net = mean(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25),
            mean_disease_burden_nonanxiety_net = mean(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75),
            mean_UF_L = mean(UF_L_prop),
            mean_UF_R = mean(UF_R_prop))
  tibble_overall_summaries_males

  #mean disease
  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_mean_disease_lm)

  anxietyGrouping_by_sex_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_by_sex_mean_disease_lm)

  #anxiety network
  anxietyGrouping_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_anxiety_net_lm)

  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_by_sex_anxiety_net_lm)

  #UF R
  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_R_lm)

  anxietyGrouping_UF_R_by_sex_lm <- lm(UF_R_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_R_by_sex_lm)

  #UF L
  anxietyGrouping_UF_L_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_L_lm)

  anxietyGrouping_UF_L_by_sex_lm <- lm(UF_L_vol ~ oAnxietydx.Meds.Inc.Dep.Collapsed*osex, data=df_demo_and_fascicles)
  summary(anxietyGrouping_UF_L_by_sex_lm)

  #burden of anxiety by network
  #clean up data frame
  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed != "unclassified") %>%
  filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
  #filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "Has.anxietydx")) %>%  #-> doesn't work
 # filter(oAnxietydx.Meds.Inc.Dep.Collapsed == c("healthy_ish", "On.Anxiolytics")) %>% #-> doesn't work
  mutate(subject = as.factor(EMPI)) %>%
#  mutate(Diagnosis = oAnxietydx.Meds.Inc.Dep.Collapsed) %>%
  mutate(Diagnosis = ifelse(oAnxietydx.Meds.Inc.Dep.Collapsed=="healthy_ish", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  #mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
  #mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
  #mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
  ##mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
  #mutate(Benzo_status = as.factor(Benzo_status)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#t test, t, t = 37.378, df = 271, p-value < 2.2e-16, anxiety net: 0.4974984; nonanxiety net: 0.256347
within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
summary(within_vs_outside_anxiety_net_t)

#t test, between diagnoses, NS, mean MS+ANXIETY = .40, MS-Anxiety = 0.37
between_dx_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
summary(between_dx_t)

#means

#mean = 0.5381082
mean_anxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
mean_anxiety_dx_anx_net

#mean = 0.2681277
mean_anxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
mean_anxiety_dx_nonanx_net

#mean = 0.4911045
mean_nonanxiety_dx_anx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Anxiety_network")])
mean_nonanxiety_dx_anx_net

#mean = 0.2544921
mean_nonanxiety_dx_nonanx_net <- mean(df_empi_dx_network_proportions$proportion_affected[which(df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety" & df_empi_dx_network_proportions$Network == "Nonanxiety_network")])
mean_nonanxiety_dx_nonanx_net

 #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
disease_within_vs_outside_anxiety_net_by_dx_groups_lmer <- lmer(proportion_affected ~ Network*Diagnosis + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)

#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
confint(disease_within_vs_outside_anxiety_net_by_dx_groups_lmer)
```

### Plot within vs outside network
```{r plottting_bar_graph}

#Within vs outside network
anxiety_net_group <- c(rep("Anxiety Network", times = dim(df_demo_and_fascicles)[1]), rep("Nonanxiety Network",times =dim(df_demo_and_fascicles)[1]))
net_values <- c(df_demo_and_fascicles$proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, df_demo_and_fascicles$proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75)

newdf <- data.frame(anxiety_net_group, net_values)

newdf <- newdf %>%
  mutate( anxiety_net_group=factor(anxiety_net_group,levels=c( "Nonanxiety Network", "Anxiety Network")))

violin_within_vs_outside_network_sum_proportion_scaled_by_network_size <- ggplot(newdf, aes(x=anxiety_net_group, y=net_values, fill=anxiety_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  ggtitle(paste0("Volume of Fascicle Disease Burden")) +
  ylab("Proportion of network affected") +
  ylim(0,1) + 
  scale_fill_manual(values=c("#D3D3D3", "#841DE2")) +
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 16, colour = "black"), axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=4/7,
        panel.background = element_rect(colour = "white", fill = "white")) + 
  coord_flip()

#display
violin_within_vs_outside_network_sum_proportion_scaled_by_network_size
```

### AnxietydxANDbenzoGroupVar within/outside network
```{r anxiety_net_intx}

### demographics
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles)
make_demographics_table_ms_anxiety(data_frame = df_demo_and_fascicles[df_demo_and_fascicles$anxietydxANDbenzoGroupVar != 0,])

#clean up data frame
df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  filter(anxietydxANDbenzoGroupVar != 0) %>% #lose 150, n now 662
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = ifelse(anxietydxANDbenzoGroupVar==1, "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Has.anxietydx = as.factor(Has.anxietydx)) %>%
  mutate(Anxiolytics_status = ifelse(On.Anxiolytics_no_beta_blocker==1, "On.Anxiolytics", "Off.Anxiolytics")) %>%
  mutate(Anxiolytics_status = as.factor(Anxiolytics_status)) %>%
  mutate(Benzo_status = ifelse(On.Benzos==1, "On.Benzos", "Off.Benzos")) %>%
  mutate(Benzo_status = as.factor(Benzo_status)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, Anxiolytics_status, Has.anxietydx, Benzo_status, PAT_AGE_AT_EXAM) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -Anxiolytics_status, -Has.anxietydx, -Benzo_status) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

#MS+Anxiety, MS-Anxiety, benzos + anxiety dx, true normal = 0.3782694; MS+ anxiety: ; MS-anxiety: 0.3672053
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"])
mean(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"])
t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS+Anxiety"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Diagnosis == "MS-Anxiety"], paired = F)

#t test, t; t = 61.356, df = 661, p-value < 2.2e-16; 95 percent confidence interval:0.2341835 0.2496681
within_vs_outside_anxiety_net_t <- t.test(df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Anxiety_network"], df_empi_dx_network_proportions$proportion_affected[df_empi_dx_network_proportions$Network == "Nonanxiety_network"], paired = T)
summary(within_vs_outside_anxiety_net_t)

 #simple lmer, NetworkNonanxiety_network  -0.241926   0.003943 661.000022  -61.36   <2e-16 ***
disease_within_vs_outside_anxiety_net_lmer <- lmer(proportion_affected ~ Network + (1|subject), data = df_empi_dx_network_proportions)
summary(disease_within_vs_outside_anxiety_net_lmer)

#Network confit:NetworkNonanxiety_network -0.2496593 -0.23419230
confint(disease_within_vs_outside_anxiety_net_lmer)

#diagnosis: NS; DiagnosisMS+Anxiety T=  0.811, p=    0.418    ; NetworkNonanxiety_network T= -49.984   p<2e-16 ***
diagnosis_by_network_interaction_lmer <- lmer(proportion_affected ~ Diagnosis*Network + (1|subject), data = df_empi_dx_network_proportions)
summary(diagnosis_by_network_interaction_lmer)

## Anxiety network x anxiolytics status
#Network (nonanxiety <anxiety network) : 
# anxiolytic status: Anxiolytics_statusOn.Anxiolytics 0.064088   0.031256 736.439692    2.05   0.0407 *  
#Mean prop affected:

## Anxiety network x benzo status
#Network (nonanxiety <anxiety network) -59.082   <2e-16; Anxiety status: T = 1.210    P = 0.227

## Anxiety network x anxiety diagnosis
#Network (nonanxiety <anxiety network) :  -51.733   <2e-16 *** ; Anxiety status:  0.721    0.471

@@

### Plot within vs outside network, matched groups
```{r plottting_bar_graph_matched}

#Within vs outside network
anxiety_net_group <- c(rep("Anxiety Network", times = dim(df_matched)[1]), rep("Nonanxiety Network",times =dim(df_matched)[1]))
net_values <- c(df_matched$proportion_volume_lost_anxiety_net_by_network_size_sum_top_25, df_matched$proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75)

newdf <- data.frame(anxiety_net_group, net_values)

newdf <- newdf %>%
  mutate( anxiety_net_group=factor(anxiety_net_group,levels=c( "Nonanxiety Network", "Anxiety Network")))

violin_within_vs_outside_network_sum_proportion_scaled_by_network_size_matched <- ggplot(newdf, aes(x=anxiety_net_group, y=net_values, fill=anxiety_net_group)) +
  geom_violin() +  
  geom_boxplot(width=0.1, color="black", fill="white", outlier.size = 0.2) + 
  ggtitle(paste0("Volume of Fascicle Disease Burden")) +
  ylab("Proportion of network affected") +
  ylim(0,1) + 
  scale_fill_manual(values=c("#D3D3D3", "#841DE2")) +
  theme(plot.title = element_text(size=16, hjust = 0.55),
        axis.text = element_text(size = 16, colour = "black"), axis.title.y  = element_blank(), 
        axis.title.x = element_text(size=16),
        axis.line = element_line(size = 1.5, colour = "black", linetype=1),
        legend.position = "none",
        aspect.ratio=4/7,
        panel.background = element_rect(colour = "white", fill = "white")) + 
  coord_flip()

#display
violin_within_vs_outside_network_sum_proportion_scaled_by_network_size_matched
```

@@

### Send anxiety groups to HYDRA ((diagnosis only + benzos)
```{r anxiety_group_prep_for_hydra}
### remake data frame from above

anxiety_vs_no_psych <- df_demo_and_fascicles %>%
  filter(anxietydxANDbenzoGroupVar != 0) %>% #get rid of the people who are not anxious and not healthy_ish, n =662, lost n=150
  filter(depGroupVar!=2) %>% #exclude people with depression , n =568, lost 104
  mutate(anxietyHydraVar = ifelse(anxietyGroupVar == 2, 1, -1)) %>%
  group_by(EMPI) %>%
  arrange(EXAM_DATE) %>%
  slice(1) %>%
  ungroup

write.csv(file=paste0(homedir, "/hydra/data/Features_anxietydxANDbenzo_prop.csv"),x=anxiety_vs_no_psych_features_for_hydra, quote = F, row.names = F)

write.csv(file=paste0(homedir, "/hydra/data/Covariates_anxietydxANDbenzo_age.csv"),x=anxiety_age, quote = F, row.names = F)

write.csv(file=paste0(homedir, "/hydra/data/Covariates_anxietydxANDbenzo_age_and_sex.csv"),x=anxiety_age_and_sex, quote = F, row.names = F)

write.csv(file=paste0(homedir, "/hydra/data/Features_anxietydxANDbenzo_yeo_prop.csv"),x=anxiety_vs_no_psych_yeo_features_for_hydra, quote = F, row.names = F)
